Cores from kicks: constraints for observations of gravitational recoil in elliptical galaxies

### 2024-01-26 papers/paper-corekick/paper-corekick.tex
Start putting figures into paper

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\ketju}{\textsc{Ketju}}
\newcommand{\mstar}{\textsc{mstar}}
\newcommand{\gadget}{\textsc{gadget-4}}

\newcommand{\Msun}{\ensuremath{\mathrm{M}_{\sun}}}
\newcommand{\kmps}{\ensuremath{\mathrm{km}\,\mathrm{s}^{-1}}}

\newcommand{\dd}[1]{\ensuremath{\mathrm{d}#1}}
\newcommand{\dv}[2]{\ensuremath{\frac{\dd{#1}}{\dd{#2}}}}
\newcommand{\vb}[1]{\ensuremath{\bm{#1}}} %vectors

@@

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{vk_rb}
    \caption{Relation and fit between core radius and kick velocity.}
    \label{fig:vkrb}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{h4}
    \caption{$h_4$ kinematic maps of pre-merger and select remnants, possible to observe signature of kick in here? (Thorsten believes yes...)}
    \label{fig:h4}
\end{figure*}

@@

%\appendix

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\ketju}{\textsc{Ketju}}                           % code name 
\newcommand{\mstar}{\textsc{mstar}}                           % code name
\newcommand{\gadget}{\textsc{gadget-4}}                       % code name

\newcommand{\Msun}{\ensuremath{\mathrm{M}_{\sun}}}            % Solar Mass
\newcommand{\kmps}{\ensuremath{\mathrm{km}\,\mathrm{s}^{-1}} }% km/s formatting
\newcommand{\Reff}{\ensuremath{R_\mathrm{e}}}                 % effective radius

\newcommand{\dd}[1]{\ensuremath{\mathrm{d}#1}}                % integral dx
\newcommand{\dv}[2]{\ensuremath{\frac{\dd{#1}}{\dd{#2}}}}     % derivative
\newcommand{\vb}[1]{\ensuremath{\bm{#1}}}                     %vectors

@@

\drafting{
    Main points to hammer home:
    \begin{enumerate}
        \item Parameters associated with the core (most importantly the core size) have a dependence on the kick velocity, whereas large-scale parameters (e.g. effective radius) do not.
        \item Increasing kick velocity induces a decrease in the overall $\langle h_4 \rangle$ profile
    \end{enumerate}
}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{rb-kick}
    \caption{
        Bayesian estimate of the merger remnant core size $r_b$, scaled to the core size of the pre-merger remnant $r_{b,0}$, as a function of kick velocity $v_\mathrm{kick}$.
        The core size distributions are shown as violin plots, with the median core size indicated by a white circle, and the interquartile range by the box. 
        Larger kick velocities are correlated with larger core sizes. Additionally, a greater spread in the distribution of core sizes over different viewing projections of the merger remnant is associated with larger kick velocities.}
    \label{fig:vkrb}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{IFU_v0000}
    \caption{
        Mock integral field unit kinematic maps of the $v_\mathrm{kick}=0\,\kmps$ remnant, plotted out to $0.5\,\Reff$. 
        Note the unordered rotation $V$, and the centrally-concentrated velocity dispersion $\sigma$.
        The majority of the merger remnant within this aperture has $h_4>0$, with a small concentration of $h_4<0$ in an annulus about the central regions.
    }
    \label{fig:IFU0}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{IFU_v0960}
    \caption{
        Mock integral field unit kinematic maps of the $v_\mathrm{kick}=960\,\kmps$ remnant, again plotted out to $0.5\,\Reff$. 
        Contrasting to the $v_\mathrm{kick}=0\,\kmps$ case in \autoref{fig:IFU0}, this IFU map has a much greater extent of $h_4<0$ that also reaches more extreme values of $h_4$ \drafting{check this}. 
    }
    \label{fig:IFU960}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{h4}
    \caption{
        Plot of the flux-weighted value of $h_4$ as a function of mean bin distance $R$ (scaled to the half mass radius) for each merger remnant simulated.
        The lines are coloured by the kick velocity. 
        Immediately apparent is the decrease in $\langle h_4 \rangle$ with increasing $v_\mathrm{kick}$.
        All merger remnants have a global minimum in $\langle h_4 \rangle$ at $R/\Reff\simeq0.2$.
    }
    \label{fig:h4}
\end{figure*}

@@

\appendix
\section{Core-Se\'rsic fit parameter estimates}
\drafting{Let's put the violin plots for all core fit parameters in the appendix}.
